\section*{Acknowledgements}
\addcontentsline{toc}{subsection}{Acknowledgements}

For supervising this thesis I would like to thank Ian Roberts and Theresa Biberauer, both of whom have been great inspirations during my time at Cambridge. I would particularly like to thank Ian for our helpful discussions in supervisions and seminars which led me down the rabbit hole of labelling, and to thank Theresa for encouraging me to apply for the MPhil course in the first instance, and for her tireless work as my Director of Studies during my undergraduate years. On that note, I would also like to extend thanks to all of my undergraduate supervisors, in particular Bert Vaux for his encouragement to delve into theoretical issues. Chris Collins gave some very useful advice and references near the start of this project, for which I am also grateful. Any remaining errors or omissions in this work are of course my own.

This work was made possible by an ESRC DTP studenship co-funded by the Harding Distinguished Postgraduate Scholars Programme Leverage Scheme, which I was incredibly lucky to receive. I would like to extend my gratitude to the Cambridge ESRC and to Theresa who aided me in my application.

I would like to thank my fellow Cambridge linguists for their stimulating discussions over the years, in particular Liam and Adam. The Undergraduate Linguistics Association of Britain has made up a not insignificant part of my life and I especialy entend my thanks to those committee members with whom I have worked for the past two years for their unending support and dedication, and to those who presented at the conference in Edinburgh this April for encouraging me to stay engaged with the diversity of the field of linguistics. A warm thank you to my friends who have made my time at Cambridge so memorable, and to my family for their continued support. Finally, thank you Lena: your boundless love and energy has made the final few months of writing this thesis all the more enjoyable.

