\section{Introduction}\label{sec:100}
\epigraph{\setstretch{1.0}\itshape [Sagredo:] It always seems to me extreme rashness on the part of some when they want to make human abilities the measure of what nature can do. On the contrary, there is not a single effect in nature, even the least that exists, such that the most ingenious theorists can arrive at a complete understanding of it. This vain presumption of understanding everything can have no other basis than never understanding anything. For anyone who had experienced just once the perfect understanding of one single thing, and had truly tasted how knowledge is accomplished, would recognize that of the infinity of other truths he understands nothing.}{\setstretch{1.0}--- Galileo, \textit{Dialogue concerning the two chief world systems} (\citeyear[101]{Galileo_1967})}

The quotidian use of language often concerns itself with the correct naming of things, be these actual objects in the world or, perhaps more accurately, objects constructed by our minds through (and in spite of) our interactions with the world. On a meta level, this same nominal curiosity extends to those abstract objects which we make use of in formulating these descriptions, the invisible structure which allows sound and sign to be associated with meaning in infinitely complex ways. \textit{A priori}, there is no reason to associate particular configurations within a structure with particular \textit{labels}, adopting the typical terminology. Rather, the conceptual necessity of labels, to the extent they are required, must be derived from observations of the natural world to which language belongs, which is no trivial task.

This thesis concerns the nature of labels within the formalised realm of natural language syntax. It will present one possible set of answers to the crucial questions: what is the nature of a syntactic label, how is it assigned, and how is it then made use of in derivations? This project is manifestly ambitious, and hence these introductory sections serve to restrict the scope of the questions being pondered in ways that are extensive, yet I believe principled. Firstly, the notion of `language' itself needs to be established and scrutinised, along with a clarification of the precise object of study: language as a part of the natural world. With this in place, guiding principles for the construction of a formal model of this natural phenomenon can be assembled, manifesting in the form of constraints and heuristics that suggest themselves from general observations and truisms. These can then be made specific in the presentation of an outline of the theory that will be adopted and adapted in the subsequent sections. This introduction therefore sets the stage for a precise formalisation of syntactic labels and the processes they are involved in, subsumed within the wider metatheoretical landscape. The focus is thus placed narrowly on theoretical and metatheoretical concerns, in a specific sense to be defined---empirical discussion of the consequences of these proposals is left for future work.

\input{11BioLeo}

\input{12MathLing}

\input{13Optimality}

\input{14Theory}

\input{15Interfaces}

\input{16Summary}
